\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}

### 2010-01-07 AffineLieAlgebras/InformalNotes/article.tex
Added some computer-programming related publications.

\theoremstyle{definition} \newtheorem{Def}{Definition}

@@

>>>>

\newtheorem{statement}{Statement}
\theoremstyle{definition} \newtheorem{Def}{Definition}

@@

For the series $A_n$ the statement has the following form:
\begin{statement}
  Consider subalgebra $\mathfrak{a}$ with the simple roots $\{\alpha_i, i=1\dots k,\; k<n\}$. Then every root $\alpha\bot \beta\in \Delta_{\mathfrak{a}}$ is the linear combination of the simple roots $\alpha_{k+2}\dots \alpha_n$ or equivalently in the language of Weyl groups, for $\forall \omega\in W: \omega\cdot W_{\mathfrak{a}}\cdot \omega=W_{\mathfrak{a}},\; \omega=r_{k+2}^{s_{k+2}}\dots r_n^{s_n}$, where $\{r_i\}$ are the Weyl reflections corresponding to simple roots $\{\alpha_i\}$.

\end{statement}
  \begin{proof}
    Assume the opposite. It is clear that it is enough to check that $r_i\cdot \omega\cdot r_i\neq \omega,\; i=1\dots k$.  
  \end{proof}
